Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-03-26 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Fix things that were preventing compilation
Update keywords
Change title to plural

\documentclass [smallextended] {svjour3} [natbib]

@@

\usepackage{calculi}
\usepackage{theorems}
\usepackage[numbers]{natbib}

@@

\title{A Variant of G\"{o}del's Ontological Proof \\
in a Natural Deduction Calculus}

@@

\noindent
\textbf{Keywords: } G\"odel's Ontological Proof, Higher-Order Modal Logics, Natural Deduction,

>>>>

%\documentclass[smallextended]{svjour3}[natbib]
\documentclass{svjour3}

@@

\usepackage{calculi}
\usepackage{theorems}
%\usepackage[numbers]{natbib}

@@

\title{Variants of G\"{o}del's Ontological Proof \\
in a Natural Deduction Calculus}

@@

\noindent
\textbf{Keywords: } Ontological Argument, Higher-Order Logics, Modal Logics, Natural Deduction.
